Figure 5 - IP-MS

### 2024-08-06 ms_figure_5_ipms.Rmd
Add FigS5

cowplot::plot_grid(
    cowplot::plot_grid(pie_bait_150 + theme(legend.position = "none"), 
                       pie_bait_150_loose + theme(legend.position = "none"), 
                       pie_bait_500 + theme(legend.position = "none"),
                       pie_bait_500_loose + theme(legend.position = "none"), nrow = 1),
    get_legend(pie_bait_150 + theme(legend.position = "bottom")),
    ncol = 1, rel_heights = c(1, 0.25)
)
```

@@

@@

>>>>

pies <- cowplot::plot_grid(
    cowplot::plot_grid(pie_bait_150 + theme(legend.position = "none"), 
                       pie_bait_150_loose + theme(legend.position = "none"), 
                       pie_bait_500 + theme(legend.position = "none"),
                       pie_bait_500_loose + theme(legend.position = "none"), nrow = 2),
    get_legend(pie_bait_150 + theme_cowplot(ft) + theme(legend.position = "bottom")),
    ncol = 1, rel_heights = c(2, 0.25)
)
```

@@

## Supplementary plot - Adn2 vs complement volcano plot

# Pho7 volcano plot

```{r}
#| warning: false

md <- metadata(sce500)
volc <- md$testres$tests$Adn2_500_plate_vs_compl_Adn2_500_plate |>
    mutate(signif = adj.P.Val < adjpThreshold & logFC > log2fcThreshold)
(adn2volc <- ggplot(volc, aes(x = logFC, y = mlog10p)) + 
        geom_text_repel(data = volc |> filter(signif),
                        aes(label = pid), min.segment.length = 0,
                        max.overlaps = Inf) + 
        geom_point(aes(alpha = signif, color = signif), 
                   show.legend = c(alpha = FALSE, color = TRUE)) + 
        scale_color_manual(values = c(`TRUE` = main_colors[5], `FALSE` = na_color), 
                           labels = c(`TRUE` = paste0("adj. p < ", adjpThreshold, 
                                                      " and logFC > ", log2fcThreshold)),
                           na.value = "black", breaks = "TRUE") + 
        scale_alpha_manual(values = c(`TRUE` = 1, `FALSE` = 0.5)) + 
        geom_point(data = volc |> dplyr::filter(pid == "Adn2") |>
                       dplyr::mutate(type = "Bait"), 
                   mapping = aes(fill = type), color = main_colors[3], 
                   shape = 21, alpha = 1, size = 2) + 
        scale_fill_manual(values = c(Bait = main_colors[3])) + 
        labs(x = "log2(fold-change)", y = "-log10(p-value)", 
             title = "Adn2 vs complement (500 mM NaCl IP-MS)") + 
        theme_cowplot(ft) + 
        theme(legend.position = "bottom") + 
        guides(color = guide_legend(nrow = 1, byrow = TRUE, title = ""),
               fill = guide_legend(nrow = 1, byrow = TRUE, title = "")))
```

## Supplementary plot - histone proteins t-stats

```{r histone-prots-500}
#| fig.width: 6
#| fig.height: 13

## Get all t-statistics and visualize
res500 <- .getTestCols(sce500, adjp_cutoff = 0.01, logfc_cutoff = 1)
histones <- res500$tstat[c("Hta1", "Htb1", "Hht2", "Hhf2"), ]
colnames(histones) <- .getProteinNameFromComparison(colnames(histones))
histones <- histones[, colnames(histones) != "Untagged"]
histones <- t(histones)
hmhistones <- Heatmap(histones, 
                      cluster_rows = TRUE, 
                      cluster_columns = FALSE, 
                      col = circlize::colorRamp2(
                          breaks = seq(1.5, 13.0, length.out = 64),
                          colors = colorRampPalette(
                              binary_heatmap_colors[c("FALSE", "TRUE")])(64)),
                      border = TRUE, 
                      border_gp = gpar(lwd = 0.5),
                      name = "Mod.\nt-stat.",
                      na_col = binary_heatmap_colors["FALSE"],
                      column_names_gp = gpar(fontsize = fl),
                      row_names_gp = gpar(fontsize = fs),
                      show_row_names = TRUE, 
                      show_column_names = TRUE, 
                      use_raster = FALSE,
                      show_heatmap_legend = TRUE, 
                      width = unit(w_ipmsHm / 1.5, "mm"), 
                      heatmap_height = unit(1.3 * h_ipmsHm, "mm"),
                      column_title_gp = gpar(fontsize = ft),
                      heatmap_legend_param = list(
                          title_gp = gpar(fontsize = fl),
                          border = "gray10",
                          border_gp = gpar(lwd = 0.5)
                      ))
set.seed(42L)
hm_histones <- grid.grabExpr(
    hmrad <- draw(hmhistones, merge_legend = TRUE,
                 heatmap_legend_side = "right",
                 annotation_legend_side = "right"),
    width = w_ipmsHm / 1.5, height = 1.3 * h_ipmsHm
)
plot_grid(hm_histones)
```

@@

## Supplementary Figure 5

```{r}
#| label: SuppFig5
#| fig.width: 10
#| fig.height: 10
#| warning: false

cowplot::plot_grid(
    cowplot::plot_grid(
        pies, 
        adn2volc, 
        ncol = 1
    ),
    hm_histones,
    nrow = 1
)
```
